---
title: "RStudio Conf. 2018 Notes"
output: html_notebook
---


Conference Website:
https://www.rstudio.com/conference/#conference


# Rstudio Conf. Day 1
---
### To the Tidyverse and Beyond: Challenges for the Future in Data Science 
### Dianne Cook


To the Tidyverse and Beyond: Challenges for the Future in Data Science 

visual inference protocol
p-hacking 
think about interactive graphics and inference procedures as part of the data pipeline

GG provides the fucntional mapping of variable to plot element that makes data plots become statistices that we can do inference on. wihc what 

xaringan package used to make slides 

catch box mics 


```{r}
# install xaringan to try
devtools::install_github('yihui/xaringan')
```

packages to look up:
blogdown


# session 1
---

### Tidy spatial data analysis 
### Edzer Pebesma

Package info:
sf package (Simple Features)
mapview package - interactive maps 
raster package 
stars

simple features fo spatial data
features -
simple features - geometric attributes

operatoins on geometries:
single 
pairs/ses

package sf - stroes simple geometries in lists
sfg: geometry for one feature

#rspatial community 

---

### The future of time series and financial analysis in the tidyverse 
### Davis Vaughan
gh: DavisVaughn
[business-science.io](http://www.business-science.io)
[github.com/business-science/presentation](http://github.com/business-science/presentation)

build packages 
Business science university 
xts vs tibble

package tidyquant - convert xts to tibble
quickly pull business financial data to tibble 
slow conversion 
limited functionality 

tibbletime package - extensions of tidy verse for timeaware tibbles through time series objects 

perform time-bases amnip on tibbles 

`collapes_by` function in tibbletime 

mapping packages ggmap, gganimate 

`rollify` function - takes a function and calls it back 



---
### infer: a package for tidy statistical inference 
### Andrew Bray

packages:
infer  
simulation through permutation
chi-squared

conducting statistica inference 
infer.netify.com
bit.ly/2DYoBOz

---
### Tidying up your network analysis with tidygraph and ggraph 
### Thomas Lin Pedersen
@thomasp85


network analysis workflow 

packages:
tidygraph - 
ggraph - viz data over ggplot2


network data, different data concept 

std workflow:
readr, tidy, dplyr, ggplot 

network analysis:
readr, tidygraph, ggraph

tidygraph extension of dyply verbs 
base is igraph package
`tbl_graph`

web scraping Marvel universe site 

look up tidygraph functions
 ggraph call - data agnostic 
 hairballs, hierarchies, hives graphs 
 


---
# Session 2


### R Markdown: Eight ways 
### Mine Cetinkaya-Rundel
bit.ly/

packages:
tint package


workflow for doing things in RStudio:

notebook
html
xaringan
blogdown
gh-doc
pdf
shiny
bookdown


students turn in on github 


---

### Creating interactive web graphics suitable for exploratory data analysis 
### Carson Sievert

---


### Beyond R: Using R Markdown with python, sql, bash, and more
### Aaron Berg

db.rstudio.com

multilingual Rmarkdown

packages:
tidyverse
reticulate
jsonlite
tidytext - for text analysis 

gutenberg

reticulate::use_python('python path', required = TRUE)



```{bash}
pwd
```

```{r}
getwd()
```


```{python}

print "Hello, Python"
```


### Branding and automating your work with R Markdown 
### Daniel Hadley

branding images 
Magick function - put gifs on top of plots 


---

weekly hours worked data averages artilce goverining.com
### Tidy eval: programming with dplyr, tidyr, and ggplot2
### Hadley Wickham


tidy eval 
save typing and translate 

!! tidyverse can use to unquote

r code is a tree 
build tress by unquoting
 expr() captures your expression 
 exper() supports unqupting - simplifying expression 
 
capture user input by qupting 

enexpr() lets you wupte user expressios 

tidy eval lets you reduce duplication 


---

### Connecting to open source databases
### Kirill Müller

packages:
RSQLite
RPostgres - literals 
RMariaDB
Rkazam
DBItest - testthat, roxygen2

bigquery, civis, MonetDBLIte, odbc, RClickhouse 

bit64 - 64bit intergers if needed data type 


R database interface DBI

quoting of identifiers and strings and literals 
distinction between queries and statements 



---

### Best practices for working with databases 
### Edgar Ruiz

packages:
DBI
odbc
dplyr
dbplyr
dbplot - new package release - cretes histograms in ggplot object 
shinydashboard - creates dashboard
purrr
shiny
highcharacter
DT
htmltools


sample flight data on SQL server 

dplyr translate to SQL
take advantage of piped code 
all code is in R 

---

# RStudio Conf Day 2
---

### Machine Learning with R and TensorFlow 
### JJ Allaire

Packages:











