---
title: "RStudio Conf. 2018 Notes"
output: html_notebook
---


Conference Website:
https://www.rstudio.com/conference/#conference


# Rstudio Conf. Day 1
---
### To the Tidyverse and Beyond: Challenges for the Future in Data Science 
### Dianne Cook


To the Tidyverse and Beyond: Challenges for the Future in Data Science 

visual inference protocol
p-hacking 
think about interactive graphics and inference procedures as part of the data pipeline

GG provides the fucntional mapping of variable to plot element that makes data plots become statistices that we can do inference on. wihc what 

xaringan package used to make slides 

catch box mics 


```{r}
# install xaringan to try
devtools::install_github('yihui/xaringan')
```

packages to look up:
blogdown


# session 1
---

### Tidy spatial data analysis 
### Edzer Pebesma

Package info:
sf package (Simple Features)
mapview package - interactive maps 
raster package 
stars

simple features fo spatial data
features -
simple features - geometric attributes

operatoins on geometries:
single 
pairs/ses

package sf - stroes simple geometries in lists
sfg: geometry for one feature

#rspatial community 

---

### The future of time series and financial analysis in the tidyverse 
### Davis Vaughan
gh: DavisVaughn
[business-science.io](http://www.business-science.io)
[github.com/business-science/presentation](http://github.com/business-science/presentation)

build packages 
Business science university 
xts vs tibble

package tidyquant - convert xts to tibble
quickly pull business financial data to tibble 
slow conversion 
limited functionality 

tibbletime package - extensions of tidy verse for timeaware tibbles through time series objects 

perform time-bases amnip on tibbles 

`collapes_by` function in tibbletime 

mapping packages ggmap, gganimate 

`rollify` function - takes a function and calls it back 



---
### infer: a package for tidy statistical inference 
### Andrew Bray

packages:
infer  
simulation through permutation
chi-squared

conducting statistica inference 
infer.netify.com
bit.ly/2DYoBOz

---
### Tidying up your network analysis with tidygraph and ggraph 
### Thomas Lin Pedersen
@thomasp85


network analysis workflow 

packages:
tidygraph - 
ggraph - viz data over ggplot2


network data, different data concept 

std workflow:
readr, tidy, dplyr, ggplot 

network analysis:
readr, tidygraph, ggraph

tidygraph extension of dyply verbs 
base is igraph package
`tbl_graph`

web scraping Marvel universe site 

look up tidygraph functions
 ggraph call - data agnostic 
 hairballs, hierarchies, hives graphs 
 


---
# Session 2


### R Markdown: Eight ways 
### Mine Cetinkaya-Rundel
bit.ly/

packages:
tint package


workflow for doing things in RStudio:

notebook
html
xaringan
blogdown
gh-doc
pdf
shiny
bookdown


students turn in on github 


---

### Creating interactive web graphics suitable for exploratory data analysis 
### Carson Sievert

packages:
Crosstalk package
Trelliscope.js
Plotly 

Geomsf
Ggplotly

Data examples 
mtcars
Gapminder 

Crosstalk linking time series 
also works with shiny

Github. Compare cpsievert/zikar, apps
Polyjs

---


### Beyond R: Using R Markdown with python, sql, bash, and more
### Aaron Berg

db.rstudio.com

multilingual Rmarkdown

packages:
tidyverse
reticulate
jsonlite
tidytext - for text analysis 

gutenberg

reticulate::use_python('python path', required = TRUE)



```{bash}
pwd
```

```{r}
getwd()
```


```{python}

print "Hello, Python"
```


### Branding and automating your work with R Markdown 
### Daniel Hadley

branding images 
Magick function - put gifs on top of plots 


---

weekly hours worked data averages artilce goverining.com
### Tidy eval: programming with dplyr, tidyr, and ggplot2
### Hadley Wickham


tidy eval 
save typing and translate 

!! tidyverse can use to unquote

r code is a tree 
build tress by unquoting
 expr() captures your expression 
 exper() supports unqupting - simplifying expression 
 
capture user input by qupting 

enexpr() lets you wupte user expressios 

tidy eval lets you reduce duplication 


---

### Connecting to open source databases
### Kirill Müller

packages:
RSQLite
RPostgres - literals 
RMariaDB
Rkazam
DBItest - testthat, roxygen2

bigquery, civis, MonetDBLIte, odbc, RClickhouse 

bit64 - 64bit intergers if needed data type 


R database interface DBI

quoting of identifiers and strings and literals 
distinction between queries and statements 



---

### Best practices for working with databases 
### Edgar Ruiz

packages:
DBI
odbc
dplyr
dbplyr
dbplot - new package release - cretes histograms in ggplot object 
shinydashboard - creates dashboard
purrr
shiny
highcharacter
DT
htmltools


sample flight data on SQL server 

dplyr translate to SQL
take advantage of piped code 
all code is in R 

---

# RStudio Conf Day 2
---

### Machine Learning with R and TensorFlow 
### JJ Allaire

packages:
keras package
tfestimators
tensorflow
lime
tfruns
cloudml
tfdeploy





creator of the Rstudio IDE, Rmarkdown pckg
tendorflow OpSrc from google 
R interface with tensorflow
deep learning uses 

tensorflow - general purpose numerical computing library
developed by google brain team for conduction machine learning 

can run on :
CPU
GPU
TPU tensor processing unit - google dev. 

supports auto differentiation 
doesn't require all data in RAM 

tendorflow models can be deployed with a low latency C++

Tensorflow basics:
tensors - data stored in multidimiensional arrays 
e.g. tensor data- vector data, (iris) 
timeseries data or sequence data - observations overtime 
4d tensor- image data 

What is flow:
dataflow graph with n nodes representing units of computation 

tensorflow or dataflow graph is generated auto from R code 
graphs gain in performance, scalability, portability 

uses of Tensorflow:
tensorflow.rstudio.com/gallery

deep learning, machine learning 

E.g. Greta project 
greta-dev.github.io/greta  - writing stat models 

deeplearning - input and putput via layers of representation 
data transformation functions parameterized by weights 
layer geometric transformaiton function on the data 
taking data - transoformations to get out close to output 

transformain ginput data into useful representations

layers of representation in a deep learning model -feature transformations are learned 

deep learning - multiple layers of representation 

other namesL 
layered represntaitons learning 
hierarchical representation of learning 

deep learning examples:
autonomous cars
human-speech level recog. 

R uses for deep learning 
does deep learning improve current R processes e.g. improving modeling 
is deep learning applicable 

how to train deep learning:
machine learning algorithms 
learning model parameters via exposure to many example data points 
eval. model and tweak it over time 

stat modeling vs. machine learning 
stats - 
machine - prediciting future data 

papers written about deep learning:
VGG millions of parameters - for computer vision 
computer vision
dl.acm.org/citation.cfm?id=2999257

arxiv.org/abs/1708.02709

time series 
ieeexplore.ieee.org/document/7870510

biomedical applications 
paper

electronic health records (EHR)
arxiv.org/abs/1801.07860

problems with deep learning:
not easily interpreted 
brittle, adversarial examples 
requires large amount of data to performwel

computationally expensive to train 

deep learning hype makes things worse
will be trolled by bad deep learning models 


keras api - promoted by google for interfacing with tensorflow, used a lot in research 
pre-process
model 
compile model
model tarining 


GPU processing
tensorflow.rstudio.com/tools/gpu

deploying models:
tensorflow serving - google

takeaways:
tensorflow is a new gen purpose numerical computing library

deep leaerning has made great progress 

R has a great set of apis for using tensorflow 

---

automl google service - in research

rstd.io/ml-with-tensorflow-and-r
tensorflow.rstudio.com/blog


---

### Teach the Tidyverse to beginners 
### David Robinson
varianceexplained.org

packages:
Fs- file system 

why teach the tidyverse

good way for students to understand thier data

datacamp - intro to the tidyverse 
data wrangline 
data viz - bring in as early as possible 
grouping summarizing 
types of viz 

case studies
data cleaning and summ with dplyr
ggplote
tidy with broom 
joining and tidy

tidy shows results immediately 
consistency in interface with functions 

what is the trade off for teaching the tidyverse:
topics taught later 
data sturctures 
loops
conditionals 
user-defined functions 

R for Data Sci book - recommendation and good example of why to teach later
those topics are covered later in - chapters 19 & 21 

have goals for what you want your students to do, and have them do it as early as possible 

talk about things students want to do 
tach abstract concepts and how they are applied 

book - text ming with R 

datacamp data driven curriculum development 

---
### Deploying TensorFlow models with tfdeploy
### Javier Luraschi


rpubs.com/jluraschi

packages:
tfdeploy
tensorflow
keras
tfestimator
cloudml
rsconnect
kerasjs



deploy models to
tensorflow serving, cloudlm, rstudio connect 

example steps:
training - export 
run tfdeploy
deploy model to rstudio connect 

---

### What makes a great R package? 
### Joseph Rickert
in github


packages:
rcpp no 1
mass no 2



CRAN 12k packages 
evaluate CRAN task views 
2960 unique task views
CRAN great resource for stats knowledge 

Good package 
does something useful for atleast a few people 
create documentations - vingettes read.me 
maintenance 
well written 
have champions promote them 

packages for reproducible reaserch and data sci:
dplyr, knitr, markdown, shiny 

CRAN_PACKAGE_DB - 

---

### Reinforcement learning in Minecraft with CNTK-R 
### Ali Zaidi 
former training team at MS 

project malmo 
github.com/mivcrosoft/malmo 


packages:
reticulate 
CNTK-R

Minecraft for experimentation 

reinforcement learning 

miner - github.com/ropenscilabs/miner | craft

Project malmo - ai research environment mod for AI experimentation 
github.com/akzaidi/malmo-docker 

---
### Differentiating by data science 
### Eric Colson

@ericcolson 


doing something better than your competitors 

differentiating in business 

e.g. saks, macy's, kmart high, mid, low 

branding e.g. LV pattern

differentiating thourgh data sci 
Stitch Fix 

algorithmns choose clothes 
algorithms-tour.stitchfix.com 



computational linguistics 
genetics algorithmns for clothes design 

most data capabiities are conceived by data scientists 



---
rOpenSci conference 

R for Data Sci book -[http://r4ds.had.co.nz/](http://r4ds.had.co.nz/)










































